HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-02-28 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
final check of author list

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-13 \\
 & & January 24, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{0.1cm}

@@

\author[c]{J Apostolakis}
\author[p]{M Asai}
\author[e]{S Banerjee}
\author[l]{R Bianchi}
\author[e]{P Canal}
\author[k]{R Cenci}
\author[b]{J Chapman}
\author[c]{G Corti}
\author[c]{G Cosmo}
\author[o]{S Easo}
\author[h]{L de Oliveira}
\author[p]{A Dotti}
\author[e,1]{V Elvira}
\author[e]{L Fields}
\author[e]{K Genser}
\author[c]{A Gheata}
\author[c]{M Gheata}
\author[c,1]{J Harvey}
\author[c]{F Hariri}
\author[e]{R Hatcher}
\author[e]{K Herner}
\author[j]{M Hildreth}
\author[c]{V Ivantchenko}
\author[e]{T Junk}
\author[e]{S-Y Jun}
\author[e]{M Kirby}
\author[m]{D Konstantinov}
\author[e]{R Kutschke}
\author[e]{P Lebrun}
\author[e]{G Lima}
\author[e]{A Lyon}
\author[h]{Z Marshall}
\author[c]{P Mato}
\author[a]{M Mooney}
\author[p]{R Mount}
\author[i]{J Mousseau}
\author[h]{B Nachman}
\author[e]{A Norman}
\author[c]{M Novak}
\author[e]{I Osborne}
\author[q]{M Paganini}
\author[e]{K Pedro}
\author[c]{W Pokorski}
\author[a]{X Qian}
\author[k]{M Rama}
\author[c]{A Ribon}
\author[c]{S Roiser}
\author[n]{D Ruterbories}
\author[e]{S Sekmen}
\author[g]{B Siddi}
\author[e]{E Snider}
\author[f]{S Vallecorsa}
\author[d]{M Verderi}
\author[e]{H Wenzel}
\author[c]{S Wenzel}
\author[a]{B Viren}
\author[e]{T Yang}
\author[e]{J Yarba}
\author[e]{L Welty-Rieger}

>>>>

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-13 \\
 & & February 28, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{0.1cm}

@@

\author[c]{J Apostolakis}
\author[p]{M Asai}
\author[e]{S Banerjee}
\author[l]{R Bianchi}
\author[e]{P Canal}
\author[k]{R Cenci}
\author[b]{J Chapman}
\author[c]{G Corti}
\author[c]{G Cosmo}
\author[o]{S Easo}
\author[h]{L de Oliveira}
\author[p]{A Dotti}
\author[e,1]{V Elvira}
\author[e]{L Fields}
\author[e]{K Genser}
\author[c]{A Gheata}
\author[c]{M Gheata}
\author[c,1]{J Harvey}
\author[c]{F Hariri}
\author[e]{R Hatcher}
\author[e]{K Herner}
\author[j]{M Hildreth}
\author[c]{V Ivantchenko}
\author[e]{T Junk}
\author[e]{S-Y Jun}
\author[e]{M Kirby}
\author[m]{D Konstantinov}
\author[e]{R Kutschke}
\author[e]{P Lebrun}
\author[e]{G Lima}
\author[e]{A Lyon}
\author[h]{Z Marshall}
\author[c]{P Mato}
\author[a]{M Mooney}
\author[p]{R Mount}
\author[i]{J Mousseau}
\author[h]{B Nachman}
\author[e]{A Norman}
\author[c]{M Novak}
\author[e]{I Osborne}
\author[q]{M Paganini}
\author[e]{K Pedro}
\author[c]{W Pokorski}
\author[a]{X Qian}
\author[e]{J Raaf}
\author[k]{M Rama}
\author[c]{A Ribon}
\author[c]{S Roiser}
\author[n]{D Ruterbories}
\author[e]{S Sekmen}
\author[g]{B Siddi}
\author[e]{E Snider}
\author[f]{S Vallecorsa}
\author[d]{M Verderi}
\author[e]{H Wenzel}
\author[c]{S Wenzel}
\author[a]{B Viren}
\author[e]{T Yang}
\author[e]{J Yarba}
\author[e]{L Welty-Rieger}
\author[p]{D.H.Wright}
